---
type: resume-source
status: active
variant: general-swe-ai
updated: '2026-06-30'
target: 'General Software Engineer roles, leaning AI/ML'
---
% !TeX program = xelatex
\documentclass{my_cv}
\title{Resume}
\author{Zachary Starnes}
\date{Jun 2026}
\usepackage[a4paper, left=2em, right=2em, top=2.5em, bottom=0em]{geometry}
\usepackage{multicol}
\setlength{\columnsep}{0cm}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage[none]{hyphenat}
\usepackage{changepage}
\usepackage{hyperref}
\usepackage{vcell}

\defaultfontfeatures{LetterSpace=2.5}

\hypersetup{
    unicode=true,
    colorlinks=true,
    urlcolor=black,
}

\setmainfont{ArialMT}[
    Path=./fonts/,
    Extension = .ttf,
    UprightFont=*-Light,
    BoldFont=*-Medium,
    ItalicFont=*-Italic,
    ItalicFeatures={
        SmallCapsFont=*-Italic,
    },
    BoldFeatures={
        SmallCapsFont=*-Medium,
    },
    SmallCapsFont=*-Medium,
    ]

\begin{document}

\begin{multicols}{2}
    \headerSection{
    \vcell{centered}
    \Huge \textbf{Zachary Starnes}
    \newline
    \badge{flashyGreen}{\Large {\textbf{Software Engineer}}}}

    \columnbreak
    \raggedleft
    \begin{spacing}{1.2}
        \large\cvParagraph{
            \vcell{centered}
            \href{tel:8438164991}{+1 843 816 4991} \\
            \href{mailto:zackhhi@gmail.com}{zackhhi@gmail.com} \\
            \href{https://aritools.xyz/}{www.aritools.xyz}
        }
    \end{spacing}
\end{multicols}

\cvSection{Education}
\begin{adjustwidth}{2em}{0em}

\positionAndCompanyLine{B.S. Computer Science}{Clemson University}{08/24 --  05/28}
\end{adjustwidth}

\setlength{\columnsep}{1cm}

\cvSection{Research}
\begin{adjustwidth}{2em}{0em}

\positionAndCompanyLine{Machine Learning Researcher}{Clemson University Creative Inquiry}{Spring 2026}

\begin{itemize}
    \item Developed and evaluated machine learning models for automated detection of predatory journals.
    \item Built and evaluated an automated classification pipeline using neural networks and open-source LLMs.
    \item Presented findings at the 21st Annual Focus on Creative Inquiry Forum and Clemson AI Research Symposium.
\end{itemize}

\techStackList{Python, PyTorch, Machine Learning, LLMs, Qwen, Llama, Classification}

\end{adjustwidth}

\cvSection{Projects}
\begin{adjustwidth}{2em}{0em}

\positionAndCompanyLine{Yuzic}{Open Source Mobile App}{12/24 -- Present}
\begin{flushleft}
    \badge{lavenderBlue}{
        \href{https://github.com/eftpmc/yuzic}{github.com/eftpmc/yuzic}
    }
\end{flushleft}

\begin{itemize}
    \item Built a cross-platform open-source music player for self-hosted media servers.
    \item Implemented offline playback, multi-server support, and music discovery.
    \item Designed a modular architecture supporting multiple self-hosted music server backends.
\end{itemize}

\techStackList{React Native, TypeScript, Expo, Redux, Express, Jellyfin API, Subsonic API}

\positionAndCompanyLine{Reddibase}{ML Answer-Extraction Pipeline}{2026}
\begin{flushleft}
    \badge{lavenderBlue}{
        \href{https://github.com/eftpmc/reddibase}{github.com/eftpmc/reddibase}
    }
\end{flushleft}

\begin{itemize}
    \item Built a source-neutral pipeline that turns Reddit discussion threads into structured answer-extraction datasets.
    \item Trained a resolved-thread classifier and semantic identifier backed by a FAISS vector index.
\end{itemize}
\techStackList{Python, PyTorch, SentenceTransformers, FAISS, FastAPI, Reddit API}

\end{adjustwidth}

\cvSection{Experience}
\begin{adjustwidth}{2em}{0em}

\positionAndCompanyLine{Freelance Software Developer}{Various Clients}{04/22 -- Present}

\begin{itemize}
    \item Built websites for Lowcountry Chorale in Lady's Island and a Hilton Head parking enforcement company.
    \item Delivered responsive layouts, contact forms, and deployment handoff for local clients.
\end{itemize}

\techStackList{React, Next.js, Node.js, TypeScript, TailwindCSS, WordPress}

\positionAndCompanyLine{Junior Developer}{Atlas Studios}{10/22 -- 06/23}

\begin{itemize}
    \item Developed object-oriented gameplay systems in Lua.
    \item Built gameplay mechanics and UI features alongside a multidisciplinary development team.
    \item Contributed to a game serving more than 10,000 players.
\end{itemize}

\techStackList{Lua, Object-Oriented Programming, Roblox Studio}

\end{adjustwidth}

\cvSection{Technical Skills}
\raggedright
\begin{adjustwidth}{2em}{0em}

\begin{itemize}
    \item \textbf{Languages:} Python, C++, C, Go, Java, JavaScript, TypeScript, Lua, Dart
    \item \textbf{Frameworks:} React, React Native, Next.js, Node.js, Express, PyTorch, Expo, TailwindCSS
    \item \textbf{Tools:} Docker, Git, Linux, MongoDB, MySQL, Redis, SQLite, Firebase, Supabase, Vercel, FAISS
\end{itemize}

\end{adjustwidth}

\end{document}
